The Role of Advection Versus Diffusion in Intraventricular Transport

### 2025-02-25 paper/main.tex
update figures 5 and 6 and plot code

Constricting the connection between the anterior and middle ventricle leads to
slower transport to the anterior ventricle (ROI 5),
and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
On the other hand, constricting the duct connecting the middle and the posterior ventricle
leads to less transport into the posterior ventricle (ROI 6),
and slightly more transport towards the anterior ventricle (ROI 5).
Faster transport to the anterior ventricle (ROI 5) and slower transport to the
posterior ventricle (ROI 6) is also the case for the geometry with a shrunk middle ventricle.
Additionally, for the latter configuration, the transport upstream of CSF flow towards the
ventral-posterior region of the middle ventricle (ROI 3) is slowed down.
For the mesh where all three ventricles are modified,
we observe higher retention of solute in the middle ventricle (ROIs 2--4),
while both the anterior and the posterior ventricles (ROIs 5 and 6) have lower mean concentrations.
Altogether, our results show that the geometry and width of the ventricular ducts matter
for solute transport. This may explain why we observed larger differences
in the cilia-deficient computational model compared to the experimental data in
\Cref{fig:fig4}, as the model and the fish have different duct diameters.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
    \caption{\textbf{a.} The original computational mesh of the ventricular geometry.
    \textbf{b.} The four modified versions of the computational geometry. Compared
    to the original mesh, the volumes of the deformed meshes are reduced by 3.9\%, 4.1\%, 1.4\% 
    and 9.4\%.
    \textbf{c.} Mean concentration $\cbar(t)$ simulated with the original and modified geometries
    in the 6 ROIs. 
    \mk{MK: How do the different geoemtries compare in terms of volume,
    areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
    \label{fig:fig6}
\end{figure}

>>>>

Constricting the connection between the anterior and middle ventricle leads to
slower transport to the anterior ventricle (ROI 5),
and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
On the other hand, constricting the duct connecting the middle and the posterior ventricle
leads to less transport into the posterior ventricle (ROI 6),
and slightly more transport towards the anterior ventricle (ROI 5).
Faster transport to the anterior ventricle (ROI 5) and slower transport to the
posterior ventricle (ROI 6) is also the case for the geometry with a shrunk middle ventricle.
Additionally, for the latter configuration, the transport upstream of CSF flow towards the
ventral-posterior region of the middle ventricle (ROI 3) is slowed down.
For the mesh where all three ventricles are modified,
we observe higher retention of solute in the middle ventricle (ROIs 2--4),
while both the anterior and the posterior ventricles (ROIs 5 and 6) have lower mean concentrations.
Altogether, our results show that the geometry and width of the ventricular ducts matter
for solute transport. This may explain why we observed larger differences
in the cilia-deficient computational model compared to the experimental data in
\Cref{fig:fig4}, as the model and the fish have different duct diameters.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
    \caption{\textbf{a.} The original computational mesh of the ventricular geometry.
    \textbf{b.} The four modified versions of the computational geometry. Compared
    to the original mesh, the volumes of the deformed meshes are reduced by 3.9\%, 4.1\%, 1.4\% 
    and 9.4\%.
    \textbf{c.} Mean concentration $\cbar(t)$ simulated with the original and modified geometries
    in the 6 ROIs.
    \textbf{d.} A comparison of the tangential cilia force in the three cilia regions
    and the total force applied. In each region, the force $F_{\mathrm{original}}$ 
    applied on the original mesh is the baseline of 100\%,
    to which the force $F_i$ of the other mesh versions are compared, where $i$ denotes
    the case. The bars for the four shrunk scenarios thus
    display $F_i/F_{\mathrm{original}}\cdot 100\%$.}
    \label{fig:fig6}
\end{figure}
